\Huge Conferences in the Era of Expensive Carbon

### 2019-08-22 main.tex
Note
COmments

\newif\ifdraft\drafttrue   % comments / todos for now
\newif\iflater\laterfalse  % comments / todos for final version

@@

@@

@@

The climate crisis is too important to ignore and too urgent to leave for
world leaders to address at their own pace: Organizations at every scale
must confront their own contributions, raise awareness among their members,
and establish new ways of doing business in the lower-carbon future that is
coming at us.  We in ACM must play our part.

>>>>

\newif\ifdraft\drafttrue    % comments / todos for now
\newif\iflater\latertrue    % comments / todos for final version

@@

\bcp{Consider all of Mike's cuts.}

\bcp{Take out details of registration data.}

@@

\bcp{Close with a discussion-starter based on the second reviewer's last
  review.}

@@

The climate crisis is too urgent to leave for
world leaders to address at their own pace: Organizations at every scale
must confront their own contributions, raise awareness among their members,
and establish new ways of doing business in the lower-carbon future that is
coming at us.  We in ACM must step up and play our part.
